%   Copyright 2012 Comet Engineering, Patrick Haring & Christian Bürgi
%
%   Licensed under the Apache License, Version 2.0 (the "License");
%   you may not use this file except in compliance with the License.
%   You may obtain a copy of the License at
%
%       http://www.apache.org/licenses/LICENSE-2.0
%
%   Unless required by applicable law or agreed to in writing, software
%   distributed under the License is distributed on an "AS IS" BASIS,
%   WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
%   See the License for the specific language governing permissions and
%   limitations under the License.

\documentclass[fontsize=12pt,
               paper=a4,
               twoside=false,
               parskip=half,
               ]{scrartcl}

% Load the packages
\input{./packages.tex}

\begin{document}

% Document title for title.tex
\newcommand{\doctitle}{Glossary}
\input{./title.tex}

\section*{Glossary}

% LaTeX does not support sorting of descriptions. Make sure to insert glossary
% items at the correct position (alphabethically sorted).
\begin{description}

\item[Bumper] \hfill \\
Round knobs that, when hit, will actively push the ball away. % by wikipedia
The player will be rewarded with points when the ball hits a bumper.

\item[Flipper] \hfill \\
Every pinball field has at least two flippers, which are levers controlled by the player. They are used for redirecting the ball up the playfield and therefor preventing it from leaving through the drain.

\item[Hole] \hfill \\
Holes on the playfield into which the player tries to direct the ball. Doing so will reward the player with points. Afterwards the ball is kicked out to bring the ball back into the game.

\item[Pinball machine] \hfill \\
A machine which allows to play pinball. It consists above all out of a playfield and input handles for manipulating the ball.

\item[Plunger] \hfill \\
The plunger is a spring-loaded rod with a small handle, used to propel the ball into the playfield. The player can control the amount of force used for launching by pulling the plunger a certain distance (thus changing the spring compression). 

\item[Ramp] \hfill \\
As the name implies, ramps are inclined planes, with a gentle enough slope that the ball may travel along it. The player attempts to direct the ball with enough force to make it to the top of the ramp and down the other side. If the player succeeds, a "ramp shot" has been made. % by wikipedia

\item[Rollover] \hfill \\
Rollovers are targets which are activated, when a ball rolls over them.

\item[Slingshot] \hfill \\
Slingshots are rubber pads which propel the ball away upon impact, like bumpers, but are usually a horizontal side of a wall. Every recent pinball machine includes slingshots to the upper left and upper right of the lowest set of flippers. % by wikipedia

\item[Stopper] \hfill \\
Also called a \emph{magic post}, this is a small pole most often found centered between and just below the lowest set of flippers. When activated (typically by hitting a specific target or targets), the pole ascends from inside the table, blocking the area between the flippers for a limited time, making it more difficult to drain and lose the ball. After time expires, it returns to its resting place just below the playfield. % by wikipedia

\item[Switch] \hfill \\
A switch is an area that is blocked off after the ball passes through it once. An example of this is the initial firing lane: as a ball passes through the firing lane, it hits a switch and cannot reenter that chute. % by wikipedia

\item[Target] \hfill \\
Targets record when a ball strikes them. The player will be rewarded with points when hitting a target.

\end{description}

\end{document}
