%   Copyright 2012 Comet Engineering, Patrick Haring & Christian Bürgi
%
%   Licensed under the Apache License, Version 2.0 (the "License");
%   you may not use this file except in compliance with the License.
%   You may obtain a copy of the License at
%
%       http://www.apache.org/licenses/LICENSE-2.0
%
%   Unless required by applicable law or agreed to in writing, software
%   distributed under the License is distributed on an "AS IS" BASIS,
%   WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
%   See the License for the specific language governing permissions and
%   limitations under the License.

\documentclass[fontsize=12pt,
               paper=a4,
               twoside=false,
               parskip=half,
               ]{scrartcl}

% Load the packages
\input{./packages.tex}

\begin{document}

% Document title for title.tex
\newcommand{\doctitle}{Supplementary Specification}
\input{./title.tex}

\tableofcontents

\section{Introduction}
In Unified Process methodology, the document \emph{Supplementary Specification} contains all the non-functional requirements. (The functional requirements are specified with \emph{Use Cases}.)

Some additional non-functional requirements are currently covered in the Vision Document.

\section{Non-functional requirements}

\subsection{Usability}
\begin{itemize}
	\item[U1] Avoid colors associated with common forms of color blindness.
	\item[U2] The interface should be as intuitive as possible.
	\item[U3] The key mapping should be customizable.
\end{itemize}

\subsection{Reliability}
\begin{itemize}
	\item[R1] When the application is closed unexpectedly the data integrity should not be harmed.
\end{itemize}

\subsection{Performance}
\begin{itemize}
	\item[P1] The application should run on entry-level computer with over 30 frames per second.
\end{itemize}

\subsection{Supportability}
\begin{itemize}
	\item[S1] The system has to run on Unix/GNU-Linux as well as on Microsoft Windows and Mac OS X.	
\end{itemize}

\section{Technical specifications}
\begin{itemize}
	\item[T1] Java 6 is used.
	\item[T2] The cross-platform game development library libgdx (http://code.google.com/p/libgdx/) is used. 
\end{itemize}

\section{Tools}
\begin{itemize}
	\item Eclipse version "Juno" for java development (http://www.eclipse.org)
	\item redmine version 2.1 for issue tracking and time reporting (http://www.redmine.org)
	\item git hosted on github for revision control (http://www.github.com)
	\item Apache maven 2 for build automation (http://maven.apache.org)
	\item Artifactory as a repository manager (http://www.jfrog.com)
	\item Astah community for UML diagrams (http://www.astah.net)
	\item Jenkins 1.499 as a Build Server (http://jenkins-ci.org)
\end{itemize}

\end{document}
